Make manuscript figures

### 2021-11-16 scripts/R/make_manuscript_figures.rmd
make correlations clearer in spvl comparison figure, ignore some manuscript-related files

Estimated trait values
TODO: think about some way of depicting phylogenetic relationships here too?
```{r}
p <- ggplot(data = spvl_values,
            aes(x = spvl_lenient_filter_first_measurement,
                y = spvl_lenient_filter_mean_measurement,
                color = spvl_strict_filter_mean_measurement)) +
        scale_color_gradient(low = "green", high = "red", name = "Mean measurement\nwith stricter filtering") +
        coord_equal() +
        geom_point() +
        labs(x = "First measurement", y = "Mean measurement") +
        shared_theme

ggsave(plot = p, filename = paste(FIGDIR, "spvl_calculation_comparison.png", sep = "/"),
       width = linewidth * 2/3, height = height * 2/3, units = "cm")

>>>>

Estimated trait values
TODO: think about some way of depicting phylogenetic relationships here too?
```{r}
comp_1 <- ggplot(data = spvl_values,
             aes(x = spvl_lenient_filter_first_measurement,
                 y = spvl_lenient_filter_mean_measurement)) +
        coord_equal() +
        lims(x = c(0, 7.25), y = c(0, 7.25)) +
        geom_point() +
        labs(x = "First measurement", y = "Mean measurement\n") +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        shared_theme

comp_2 <- ggplot(data = spvl_values,
               aes(x = spvl_lenient_filter_first_measurement,
                   y = spvl_strict_filter_mean_measurement)) +
        coord_equal() +
        lims(x = c(0, 7.25), y = c(0, 7.25)) +
        geom_point() +
        labs(x = "First measurement", y = "Mean measurement\nwith stricter filtering") +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        shared_theme

comp_3 <- ggplot(data = spvl_values,
                 aes(x = spvl_lenient_filter_mean_measurement,
                     y = spvl_strict_filter_mean_measurement)) +
        coord_equal() +
        lims(x = c(0, 7.25), y = c(0, 7.25)) +
        geom_point() +
        labs(x = "Mean measurement", y = "Mean measurement\nwith stricter filtering") +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        shared_theme

comp <- cowplot::plot_grid(comp_1, comp_2, comp_3, nrow = 1)

ggsave(plot = comp, filename = paste(FIGDIR, "spvl_calculation_comparison.png", sep = "/"),
       width = linewidth, height = height * 2/3, units = "cm")
